OptiFit project update

### 2020-12-14 docs/slides/2020-12-14_lab-mtg.Rmd
Add links (post-meeting)

>>>>

# Useful links

- [these slides (R Markdown)](https://github.com/SchlossLab/OptiFitAnalysis/blob/master/docs/slides/2020-12-14_lab-mtg.Rmd)
- [these slides (HTML)](http://www.schlosslab.org/OptiFitAnalysis/slides/2020-12-14_lab-mtg.html#1)
- [my code club on unit testing in R](https://github.com/SchlossLab/intro-testing-r)
- [`assertthat` R package](https://github.com/hadley/assertthat)
- [Jenny Bryan’s talk on debugging R code](https://rstudio.com/resources/rstudioconf-2020/object-of-type-closure-is-not-subsettable/)
